\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
%\usepackage{settings}
\RequirePackage[backend=biber, style=year, sorting=none,giveninits=true,
maxbibnames=50, eprint=false,
backref=true, backrefstyle=three]{biblatex}
\usepackage{xstring}
\RequirePackage{fontawesome}

% Second parameter can be anything, as the headings are added separately
\renewcommand*{\mkbibcompletename}[1]{
  \ifitemannotation{jointfirst}
    {\IfSubStr{#1}{Barkmann}{\textbf{#1*}}{#1*}}
    {\IfSubStr{#1}{Barkmann}{\textbf{#1}}{#1}}                
}

% Define custom bibliography driver for articles
\DeclareBibliographyDriver{article}{%
  \usebibmacro{bibindex}%
  % Create table-like format with year on left, content on right
  \begin{tabular}[t]{@{}p{0.8cm}@{\hspace{0.5cm}}p{0.85\textwidth}@{}}
    \printfield{year} & 
    \begin{minipage}[t]{\linewidth}
      \textbf{\printfield[titlecase]{title}}\\
      \printnames{author}\\
      \iffieldundef{note}{}{\textbf{\printfield{note}} at }\textit{\usebibmacro{journal}}
    \end{minipage}
  \end{tabular}%
  \vspace{0.1cm}
}

% Custom formatting for journal titles
\DeclareFieldFormat[article]{journaltitle}{#1}
\DeclareFieldFormat[article]{title}{#1}

% Remove quotes from titles
\DeclareFieldFormat[article]{title}{#1}

\addbibresource{mybib.bib}

\name{Florian Barkmann} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{\href{flobarkmann@gmail.com}{{{\small\faEnvelopeO}~}flobarkmann@gmail.com} \\ \href{https://florianbarkmann.github.io}{{{\small\faGithub}~}florianbarkmann.github.io}}  %

\begin{document}
  
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf PhD Student at Boeva Lab}, ETH Zürich \hfill {Aug. 2022 -- \textcolor{white}{July 2022}}\\
{\bf Data Science (M.Sc.)}, ETH Zürich \hfill {Oct. 2020 -- July 2022}\\
%GPA: 5.68 (from 6, best, to 1, worst)\\
{\bf Mathematics (B.Sc.)}, Eberhard Karls University Tübingen \hfill {Oct. 2015 -- Oct. 2019}\\
{\bf International Economics (B.Sc.)}, Eberhard Karls University Tübingen \hfill {Oct. 2014 -- Oct. 2018}\\
%GPA: 1.22 (from 1, best, to 5, worst)
\end{rSection}
\begin{rSection}{EXPERIENCE}
\textbf{Cradle} \hfill Sep. 2025 -- Jan. 2025\\
Machine learning research intern \hfill \textit{Zürich, Switzerland}\\
\textbf{German Cancer Research Center} \hfill Feb. 2020 -- July 2020\\
Research intern hosted by Niklas Wahl \hfill \textit{Heidelberg, Germany}\\
\textbf{German Climate Computing Center} \hfill Oct. 2019 -- Feb. 2020\\
Intern \hfill \textit{Hamburg, Germany}


\end{rSection}
\begin{rSection}{PUBLICATIONS}
\end{rSection}
\vspace{-0.75cm}
\subsection*{Journal articles}
\printbibliography[keyword={press},heading={none}]
\vspace{-0.35cm}
\subsection*{Proceedings}
\printbibliography[keyword={proceedings},heading={none}]
\vspace{-0.35cm}
\subsection*{Peer-reviewed workshop papers}
\printbibliography[keyword={workshop},heading={none}]
\vspace{-0.35cm}
\subsection*{Preprints}
\printbibliography[keyword={preprint},heading={none}]
* denotes shared first authorship.


\begin{rSection}{CONFERENCE CONTRIBUTIONS}
 
\begin{enumerate}
\item[2024] AccMLBio workshop at ICML, Vienna, \textbf{Spotlight talk}
\item[2023] Single cell, systems biology and data analytics approaches to understand cellular mechanisms in development and disease, Freiburg, \textbf{Contributed talk}
\item[2023] Basel Computational Biology Conference (BC2), Basel, \textbf{Contributed talk}
\item[2022] Single Cell Genomics meets Data Science, Munich, \textbf{Contributed talk}, \textbf{best poster award}
\item[2021] 7th Annual Loma Linda workshop on Particle Imaging and Radiation Treatment Planning, Loma Linda, \textbf{Contributed talk}
\end{enumerate}
\end{rSection}

\begin{rSection}{TEACHING RESPONSIBILITIES}
\vspace{-1.25em}
\item Computational Intelligence Lab \textbf{(Head TA)}, ETH Zürich \hfill {Feb. 2025 -- Oct. 2025}
\item Advanced Machine Learning, ETH Zürich\hfill {Oct. 2024 -- Feb. 2025}
\item Computational Intelligence Lab \textbf{(Head TA)}, ETH Zürich \hfill {Feb. 2024 -- Oct. 2024}
\item Advanced Machine Learning, ETH Zürich\hfill {Oct. 2023 -- Feb. 2024}
\item Computational Intelligence Lab, ETH Zürich \hfill {Feb. 2023 -- Oct. 2023}
\item Deep Learning, ETH Zürich\hfill {Oct. 2022 -- Feb. 2023}
\item Machine Perception, ETH Zürich \hfill {Feb. 2022 -- Oct. 2022}
\end{rSection}
\begin{rSection}{SUPERVISION}
\begin{enumerate}
    \item[2025] Flavia Pedrocchi, Master Thesis, \textit{Interpretable Features in Single-Cell Foundation Models via Sparse Autoencoders} (current)
    \item[2025] Katya Tubis, Research intern, \textit{Delta Tuning Methods for parameter efficient fine-tuning of Single-Cell Foundation Models} (current)
    \item[2024] Alexander Theus, Master Thesis, \textit{scCancerGPT: Understanding intratumor heterogeneity through scRNA-seq foundation models}, \textbf{Paper accepted} at NeurIPS 2024 Workshop: AIDrugX 2024
    \item[2024] Marco Baumann, Bachelor Thesis, \textit{scDIVA: Towards domain invariant reference-query mapping}, \textbf{Poster presentation} at scverse conference 2024
    \item[2024] Fiona Muntwyler joint supervision with Imant Daunhawer, Master Thesis, \textit{Multi-modality integration using VAEs}
    \item[2024] Olga Ovcharenko joint supervision with Imant Daunhawer, Master Thesis, \textit{Self-Supervised contrastive Learning for spatial transcriptomics data}, \textbf{Paper accepted} to NeurIPS 2024 Workshop: Self-Supervised Learning 2024
    \item[2023] Philip Toma, Master Thesis, \textit{Regularized Self-Supervised Learning from Nearest Neighbors to Integrate scRNA-seq Experiments},
    \textbf{Paper accepted} to NeurIPS 2024 Workshop: Self-Supervised Learning 2024
    \item[2023] Leander Diaz-Bone, Bachelor Thesis, \textit{VAEs with Learnable Priors for Learning a Robust Latent Space Representation of Single-Cell RNA Sequencing Data}, \textbf{Poster presentation} at Single cell, systems biology and data analytics conference in Freiburg 2023
\end{enumerate}
\end{rSection}

\begin{rSection}{OTHER ACTIVITIES}
\vspace{-1.25em}
\item Reviewer for \textit{ICLR} (2026), \textit{SIMBIOCHEM@EurIPS} (2025),\textit{MMRL4H@EurIPS} (2025), \textit{GenBio@ICML} (2025), \textit{MLGenX@ICLR} (2025, 2026), \textit{Cancer Discovery} (2024), \textit{AIDrugX@NeurIPS} (2024), \textit{Bioinformatics}(2022)
\item Co-organizer of quarterly meetings for all bioinformatics groups from ETH Zürich\hfill {Oct. 2022 -- Oct. 2023}\\ and the University of Zürich
\item Semester abroad at the University of Hong Kong\hfill {Oct. 2016 -- Dec. 2016}
\item Volunteering at a school in San José, Costa Rica\hfill {Aug. 2013 -- Aug. 2014}
\end{rSection} 

\nocite{ahlmann2026representation,barkmann2025cansig,ciernik2023ans,prummer2023scroshi,barkmann2023superiorization,ovcharenko2025scsslbench,theus2024cancerfoundation,vandenhirtz2024sctree,pedrocchi2025sparse,kraft2025cdstate}
\end{document}
 